Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-10-21 referee.tex
Revising response to the first issue

The 10 pc quoted above is a parameter called StarClusterCombineRadius, and controls how many stars form within a certain spatial range. Within our original simulation, this parameter was set to 10 pc, meaning that all stars younger than 10 kyr and within 10 pc of each other are merged into a single star. To make sure that this value does not affect our results, we have run simulations for a range of this parameter, namely from 0.625 pc to the original 10 pc. The simulations are a 1 comoving Mpc$^3$ box, zoomed-in on a single halo with a mass of $10^{5.8} M_{\odot}$ at the end of the run. The simulations run for a total of 10 Myr. We see the same number of Pop III stars form regardless of the chosen value for the merging parameter. Thus, our results are independent of this value. This detail has been added to section 2.2.1.

--May still need to answer the questions ``Which is the motivation for the length scale of 1 pc?''

>>>>

The 10 pc quoted above is a parameter called \texttt{StarClusterCombineRadius}, and controls whether newly formed star particles will be merged within a certain radius. Within our original simulation, this parameter was set to 10 pc, meaning that all stars younger than 10 kyr and within 10 pc of each other are merged into a single star particle.  The 10 kyr timescale originates from the approximate protostellar timescale when the ionizing luminosity is linearly increased to its ZAMS value. We chose a value of 10 pc because it corresponds to the approximate radius where H$_2$ formation allows the gas to cool from the halo's virial temperature (e.g. Yoshida et al. 2006).

To ensure that this value does not affect our results, we have run a suite of test simulations for a range of this parameter, namely from 0.625 pc, increasing by a factor of two up to the original 10 pc. The simulations are a 1 comoving Mpc$^3$ box with the same mass and spatial resolution and physics set, zoomed-in on a single halo with a mass of $10^{5.8} M_{\odot}$ at the end of the run. The simulations run for a total of 10 Myr after the first star forms. We see the same number of Pop III stars form regardless of the chosen value for the merging parameter. Thus, we conclude that our results are independent of this value. We have added these details to Section 2.2.1.
